% Discussion
% Covers: interpretation of results, broader applicability, lessons learned, threats to validity, limitations
% See .claude/concept.md section 9 for anticipated threats.

\label{sec:discussion}

\subsection{Interpretation of Results}

The evaluation results collectively support the claim that the phase-based meta-model captures the administrative structure of project-based courses more completely than existing tools, and that PROMPT operationalizes this model in a usable, valued platform.

\subsubsection{RQ1 Discussion}

The feature comparison demonstrates that PROMPT fills a genuine capability gap:
no existing tool provides native support for the combination of phase lifecycle modeling, formative assessment, and plugin-based extension that project-based courses require.
The multi-semester deployment at \university{} confirms that the meta-model is not only theoretically adequate but operationally sufficient for a complex, high-stakes practical course.

\subsubsection{RQ2 Discussion}

The dominant interview theme -- workflow consolidation -- confirms the core motivation for PROMPT's design:
instructors were maintaining unnecessary tool fragmentation, and a unified phase-based platform directly addresses this overhead.
The setup overhead identified as the primary pain point is an expected cost of the platform's flexibility and points to a concrete future work direction: phase configuration templates and semester-to-semester course cloning.

\subsubsection{RQ3 Discussion}

Student survey results indicate strong perceived usability and high appreciation of the Assessment Phase's formative feedback features;
the high ratings for ``criteria were clearly communicated'' and ``self-evaluation supported reflection'' confirm the pedagogical value of the Assessment Phase's design beyond its administrative function.

\subsection{Broader Applicability Beyond Computing Education}

The phase-based meta-model's domain-agnostic design means the administrative benefits demonstrated in computing education generalize to any discipline with project-based teaching.
A business capstone program can configure PROMPT with an Application Phase for student project preferences, a Team Phase for advisor-driven formation, and an Assessment Phase with business-specific criteria (market analysis quality, presentation skills, professional conduct).
An engineering design course can model the iterative design-build-test cycle as a sequence of Assessment Phases, with criterion sets tailored to each design stage.
A healthcare simulation course can use the Interview Phase to assign students to simulation scenarios and the Assessment Phase to formalize clinical competency rubrics with self-reflection components.
The Assessment Phase's configurable criteria are the key enabler of this generalizability:
instructors adapt the same infrastructure to discipline-specific evaluation norms without any platform modification.

\begin{recommendationBox}
Instructors of any project-based course with a structured milestone lifecycle should consider PROMPT as an alternative to ad-hoc tool combinations; the Assessment Phase configuration is the first step to formalizing formative feedback practices.
\end{recommendationBox}

\subsection{Lessons Learned}

Adopting a micro-frontend architecture provided the deployment independence required by the phase plugin model but introduced significant operational complexity:
each phase requires its own container, CI pipeline, and versioning, increasing DevOps overhead compared to a monolithic deployment.
For institutions without Kubernetes expertise, this overhead may be a barrier to adoption -- a Docker Compose deployment mode is maintained for simpler setups.
The decision to give each phase an independent database schema proved correct for phase isolation but complicated cross-phase queries (e.g., reporting on a student's full course trajectory), which required a dedicated aggregation layer.

\subsection{Threats to Validity}

\subsubsection{Internal Validity}

A primary threat to internal validity is the feature comparison's reliance on author-defined criteria and scoring, introducing potential bias toward capabilities that PROMPT provides.
The interview participants were all PROMPT users recruited from \university{}, creating a selection bias toward individuals with a positive predisposition toward the tool.

\subsubsection{External Validity}

The empirical evaluation is limited to a single institution (\university{}) and a single course type (iPraktikum), limiting the generalizability of the usability and utility findings to other institutional contexts and disciplines.
The multi-institution adoption evidence partially mitigates this threat, but empirical cross-disciplinary validation remains future work.

\subsubsection{Construct Validity}

The \acrshort{sus} provides a validated measure of perceived usability but does not capture domain-specific utility;
the custom Likert items address phase-specific utility but lack external validation.
Interview themes reflect instructor perceptions rather than objective behavioral data, and the reported time savings are estimates rather than measured values.

\subsection{Limitations}

The evaluation does not include longitudinal data on learning outcomes associated with PROMPT-supported formative assessment, leaving open the question of whether the Assessment Phase's design translates to improved student performance or reflection quality.
Instructor interview participants were recruited from a single institution and all had substantial experience with PROMPT, limiting the perspective of first-time adopters.
The extensibility claim is supported primarily by internal phase development evidence;
independent third-party implementation of custom phases would provide stronger validation of the plugin architecture.
